\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-12-04 background.tex
code style changed

\begin{figure}[t!]
% \centering
\begin{SubFloat}{\label{fig:2a}Simple SystemJ program}%...verbatim subfigure
\begin{minipage}[b]{0.3\linewidth}% a minipage to control the width...
  \begin{scriptsize}
\begin{verbatim}
{
int counter = 0;
while(true){
 abort(immediate A){
  while(true) pause; 
 } // abort end
  emit O;
  if(counter != 0) { // java computation leading to WCRT}
  ++counter;
 } // loop end
} // SystemJ CD end
\end{verbatim}%
  \end{scriptsize}
\end{minipage}%
\end{SubFloat}
\hspace{1.5cm}%
% \begin{SubFloat}[Black box]{\label{fig:2b}Logical time in SystemJ}%
% \includegraphics[scale=0.4]{moc}
% \end{SubFloat}%
% \vspace{-10pt}

>>>>

\begin{figure}[t!]
% \centering
\begin{SubFloat}{\label{fig:2a}Simple SystemJ program}%...verbatim subfigure
\begin{minipage}[b]{1\linewidth}% a minipage to control the width...
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
{
int counter = 0;
while(true){
 abort(immediate A){
  while(true) pause; 
 } // abort end
  emit O;
  if(counter != 0) { // java computation leading to WCRT}
  ++counter;
 } // loop end
} // SystemJ CD end
\end{lstlisting}%
\end{minipage}%
\end{SubFloat}
\hspace{1.5cm}%
% \begin{SubFloat}[Black box]{\label{fig:2b}Logical time in SystemJ}%
% \includegraphics[scale=0.4]{moc}
% \end{SubFloat}%
% \vspace{-10pt}

### 2013-12-04 delays.tex
code style changed

\begin{figure}[tb]
    \begin{minipage}{\textwidth}
      \begin{scriptsize}
\begin{verbatim}
trap(T){
 int x = 0;
 while(true){
  x = x + 1;
  pause;
  if(x == d) exit (T); //wait for "d" ticks
 } // d is the number of logical ticks calculated
} // by Algorithm 1
\end{verbatim}
      \end{scriptsize}
    \end{minipage}
    \caption{The rewrite of \texttt{delay} construct}
    \label{fig:3}
\end{figure}

>>>>

\begin{figure}[tb]
	\vspace{-10pt}
    \begin{minipage}{\textwidth}
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
trap(T){
 int x = 0;
 while(true){
  x = x + 1;
  pause;
  if(x == d) exit (T); //wait for "d" ticks
 } // d is the number of logical ticks calculated
} // by Algorithm 1
\end{lstlisting}
    \end{minipage}
    \caption{The rewrite of \texttt{delay} construct}
    \label{fig:3}
\end{figure}

### 2013-12-04 discussion.tex
code style changed

\begin{figure}[h!]
  \centering
    \begin{minipage}[b]{\linewidth}
\begin{verbatim}
// timeout after 1ms.
trap(T){{await(A);}||
        {delay(1 ms);exit(T);}}
\end{verbatim}
    \end{minipage}
  \caption{Programming low priority timeout tasks with delay statements}
  \label{fig:timeout}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{\linewidth}
\begin{verbatim}
while(true) { delay ((1..1)ms); emit S; 
 //do something }
\end{verbatim}
  \end{minipage}
  \caption{Programming periodic tasks with delay statements}
  \label{fig:periodic}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{SubFloat}{\label{pp:a}Original program}
    \centering
    \begin{minipage}[b]{0.3\linewidth}
\begin{verbatim}
while(true) {
 delay(1..1 ms);
 //extra pause
 pause;
 emit S;
}
\end{verbatim}
  \end{minipage}
\end{SubFloat}
\hspace{9pt}
  \begin{SubFloat}{\label{pp:b}Rewritten program}
    \begin{minipage}[h]{0.5\linewidth}
\begin{verbatim}
while(true) {
 while(true) { 
  trap(T) {
   int x = 0;
   while(true) {
    x = x + 1;
    pause;
    if (x == d)
     exit(T);
   }
  }
  //extra pause
  pause;
  emit S;
 }
}
\end{verbatim}
    \end{minipage}
  \end{SubFloat}
\caption{Extra pause statements in periodic tasks}
  \label{fig:periodic2}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{\linewidth}
\begin{verbatim}
suspend(S) {
 emit START_TIMER(10); 
 await (TIMER);emit O1;
}
\end{verbatim}
  \end{minipage}
  \caption{Interaction of preemption and external timers}
  \label{fig:preemp}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
			\vspace{-10pt}
			\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={await,emit,trap,pause,exit,delay}]
// timeout after 1ms.
trap(T){{await(A);}||
        {delay(1 ms);exit(T);}}
\end{lstlisting}
  \caption{Programming low priority timeout tasks with delay statements}
  \label{fig:timeout}
			\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay}]
while(true) { delay ((1..1)ms); emit S; 
 //do something }
 \end{lstlisting}
  \caption{Programming periodic tasks with delay statements}
  \label{fig:periodic}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{SubFloat}{\label{pp:a}Original program}
    \centering
			\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay}]
while(true) {
 delay(1..1 ms);
 //extra pause
 pause;
 emit S;
}
\end{lstlisting}
\end{SubFloat}
\hspace{9pt}
  \begin{SubFloat}{\label{pp:b}Rewritten program}
			\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay}]
while(true) {
 while(true) { 
  trap(T) {
   int x = 0;
   while(true) {
    x = x + 1;
    pause;
    if (x == d)
     exit(T);
   }
  }
  //extra pause
  pause;
  emit S;
 }
}
\end{lstlisting}
  \end{SubFloat}
\caption{Extra pause statements in periodic tasks}
  \label{fig:periodic2}
\end{figure}

@@

\begin{figure}[h!]
  \centering
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,basicstyle=\normalsize\ttfamily,morekeywords={emit,trap,pause,exit,delay,suspend}]
suspend(S) {
 emit START_TIMER(10); 
 await (TIMER);emit O1;
}
		\end{lstlisting}
  \caption{Interaction of preemption and external timers}
  \label{fig:preemp}
	\vspace{-10pt}
\end{figure}

### 2013-12-04 exps.tex
code style changed

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time delays and program sizes are shown in
Table~\ref{fig:benchlist}.
{\renewcommand{\arraystretch}{0.9}
\begin{table}[h!]
	\small
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{delay(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{delay(2.4..2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 & \texttt{delay(1.667..1.667 ms)}      &                    &                      \\ 
											 & \texttt{delay(0.05..0.05 ms)}       &                    &                      \\ 
											 & \texttt{delay(0.3..0.3 ms)}        &                    &                      \\ 
											 & \texttt{delay(0.733..0.733 ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{delay(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{delay(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{delay(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{2}{*}{AECS} & \texttt{delay(10000 ms)} ($CD1$) 
& \multirow{2}{*}{2} & \multirow{2}{*}{267} \\
& \texttt{delay(10000..10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\end{table}
}
{\renewcommand{\arraystretch}{0.6}
\begin{table*}[t!]
\centering
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0.0396 ms	& 0.0425 ms & 0.0190 ms &
	0.0263 ms & 0.1784 ms & 0.1284 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.1152 ms & 0.1096 ms & 0.0647 ms
	& 0.0491 ms & 0.3476 ms & 0.2991 ms\\ 
	\cmidrule(r){1-8}

@@

\begin{figure}[h!]
  \begin{SubFloat}{\label{delaycode:a}Original program}
    \centering
    \begin{minipage}[b]{0.3\linewidth}
      \scriptsize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
    \end{minipage}
  \end{SubFloat}
  \hspace{1cm}%
  \begin{SubFloat}{\label{delaycode:b}Program with delay constructs}
    \centering
    \begin{minipage}[b]{0.5\linewidth}
      \scriptsize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(10000 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\begin{SubFloat}{\label{fig:improv-a}Original program}
    \begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
if(E.isValiedRequest(id)){
  // code ..
}
\end{verbatim}
\end{minipage}
\end{SubFloat}
  \hspace{1cm}%
  \begin{SubFloat}{\label{fig:improv-b}Program with reduced WCRT}
    \centering
    \begin{minipage}[b]{0.35\linewidth}
      \scriptsize
\begin{verbatim}
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
pause; // Inserting pause
if(E.isValiedRequest(id)){
  // code ..
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
	\caption{Improving WCRT by shortening a critical path}
	\label{fig:improv}
\end{figure}

>>>>

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time delays and program sizes are shown in
Table~\ref{fig:benchlist}.
{\renewcommand{\arraystretch}{0.9}
%\renewcommand{\texttt}[1] {\begin{lstlisting}[language=Java,morekeywords={delay}] #1 \end{lstlisting}}
\begin{table}[h!]
	\small
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{delay(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{delay(2.4..2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 & \texttt{delay(1.667..1.667 ms)}      &                    &                      \\ 
											 & \texttt{delay(0.05..0.05 ms)}       &                    &                      \\ 
											 & \texttt{delay(0.3..0.3 ms)}        &                    &                      \\ 
											 & \texttt{delay(0.733..0.733 ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{delay(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{delay(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{delay(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{2}{*}{AECS} & \texttt{delay(10000 ms)} ($CD1$) 
& \multirow{2}{*}{2} & \multirow{2}{*}{267} \\
& \texttt{delay(10000..10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\end{table}
}
{\renewcommand{\arraystretch}{0.6}
\begin{table*}[t!]
\centering
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0.0396 ms	& 0.0425 ms & 0.0190 ms &
	0.0263 ms & 0.1784 ms & 0.1284 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.1152 ms & 0.1096 ms & 0.0647 ms
	& 0.0491 ms & 0.3476 ms & 0.2991 ms\\ 
	\cmidrule(r){1-8}

@@

\begin{figure}[h!]
	\vspace{-10pt}
  \begin{SubFloat}{\label{delaycode:a}Original program}
    \centering
      \scriptsize
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{lstlisting}
  \end{SubFloat}
  \hspace{1cm}%
  \begin{SubFloat}{\label{delaycode:b}Program with delay constructs}
    \centering
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(10000 ms);
    exit(T);  
  }
}
\end{lstlisting}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\vspace{-10pt}
	\begin{SubFloat}{\label{fig:improv-a}Original program}
    \begin{minipage}[b]{0.45\linewidth}
		\begin{lstlisting}[style=sysj,morekeywords={present,emit,trap,pause,exit,delay,suspend}]
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
if(E.isValiedRequest(id)){
  // code ..
}
\end{lstlisting}
\end{minipage}
\end{SubFloat}
  \begin{SubFloat}{\label{fig:improv-b}Program with reduced WCRT}
    \centering
    \begin{minipage}[b]{0.45\linewidth}
		\begin{lstlisting}[style=sysj,morekeywords={emit,present,trap,pause,exit,delay,suspend}]
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
pause; // Inserting pause
if(E.isValiedRequest(id)){
  // code ..
}
\end{lstlisting}
		\end{minipage}
	\end{SubFloat}
	\caption{Improving WCRT by shortening a critical path}
	\label{fig:improv}
	\vspace{-10pt}
\end{figure}

### 2013-12-04 motivation.tex
code style changed

% system{
%  interface{
%   input signal TOUCH;
%   output signal GREEN_LIGHT;
%   output char channel S;
%   input char channel R;
%  }
\begin{figure}[t!]
% \begin{center}
\begin{minipage}{5cm}
  \begin{scriptsize}

\begin{verbatim}
{ // Clock-domain 1
while(true) {
  trap(TRAP){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;} //reaction R1
    || // synchronous parallel operator
    {
     //exit after any where from 50.3 to 200.3 ms.
     delay (50.3 .. 200.3 ms); 
     exit(TRAP); 
    } // reaction R2
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; // only construct to consume logical time
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(true){ receive S; // do something with S}
}
\end{verbatim}
  \end{scriptsize}
\end{minipage}
\caption{An example human responsiveness system (HRTCS)}
% }
% \end{center}
\label{fig:1}
\end{figure}

>>>>

% system{
%  interface{
%   input signal TOUCH;
%   output signal GREEN_LIGHT;
%   output char channel S;
%   input char channel R;
%  }
\begin{figure}[t!]
% \begin{center}
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,morekeywords={sustain,send,receive,abort,await,emit,present,trap,pause,exit,delay,suspend}]
{ // Clock-domain 1
while(true) {
  trap(TRAP){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;} //reaction R1
    || // synchronous parallel operator
    {
     //exit after any where from 50.3 to 200.3 ms.
     delay (50.3 .. 200.3 ms); 
     exit(TRAP); 
    } // reaction R2
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; // only construct to consume logical time
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(true){ receive S; // do something with S}
}
\end{lstlisting}
\caption{An example human responsiveness system (HRTCS)}
% }
% \end{center}
\label{fig:1}
\end{figure}
